\documentclass[11pt]{article}
\usepackage{enumerate}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{tabularx}

\pagestyle{empty} \setlength{\parindent}{0mm}
\addtolength{\topmargin}{-0.5in} \setlength{\textheight}{9in}
\addtolength{\textwidth}{1.75in} \addtolength{\oddsidemargin}{-0.9in}

\title{Sumerian Project\\
		Team Work Plan\\
		CS 491}
\author{Danielle Thurow \\
		  Seoung Jung\\
		  Zachary Fox\\
		  Thomas Fritchman}
\date{}

\begin{document}
\maketitle
\newpage

\tableofcontents
\newpage

\begin{center}
\Large Revision History\\
\begin{tabularx}{\textwidth}{|c|X|c|}
	\hline
	\textbf{Revision} & \textbf{Description} & \textbf{Date}\\ \hline
	1.0 & Initial Document & 5/1/2014\\ \hline
\end{tabularx}
\end{center}
\newpage

\section{TEAM CHARTER}
\subsection{TEAM MEMBERS}
\textbf{Project Manager} - Seoung Jung\\
\textbf{Software Test Lead} - Danielle Thurow\\
\textbf{Software Developer Lead} - Zachary Fox\\
\textbf{Quality Assurance} - Thomas Fritchman

\subsection{TEAM ROLES/RESPONSIBILITIES}
\begin{tabularx}{\textwidth}
			{|l|X|X|X|X|X|X|X|X|X|}
    \hline
    & 
    \rotatebox{270}{Contact} & 
    \rotatebox{270}{Writeup} & 
    \rotatebox{270}{Attend Meetings} & 
    \rotatebox{270}{Requirements / SRS} & 
    \rotatebox{270}{Repository} & 
    \rotatebox{270}{Planning} & 
    \rotatebox{270}{Process Monitor} & 
    \rotatebox{270}{Document Consistency Assurance} &
    \rotatebox{270}{Meeting Minutes}\\
    \hline
    Seoung Jung             & X &   & X & X &   &   &   &   & X \\
    Danielle Thurow         & X &   & X & X & X &   &   &   &   \\
    Zachary Fox             &   & X & X & X &   &   & X &   &   \\
    Thomas Fritchman        &   & X & X & X &   & X &   & X &   \\
    \hline
\end{tabularx}


\subsection{CONTACTS}
\begin{itemize}
	\item 493 Group - Danielle
	\item Dr. Hearne - Danielle
	\item Dr. Garfinkle - Danielle
	\item Aran Clausen - Seoung
	\item Dr. Yudong Liu - Seoung
	\item Other resources - Seoung
\end{itemize}
    
\subsection{TEAM RULES}
\begin{itemize}
	\item Treat each other with respect.
	\item Allow all individuals and ideas to be heard.
	\item Keep an open mind.
	\item Follow through with agreed upon areas of responsibility.
\end{itemize}

\section{TASK}
\subsection{PROJECT ABSTRACT}
???\\
Resources??

\section{TIMETABLE/CHECKPOINTS}
\textbf{Weekly Schedule}\\
Mondays at 3:30 - Meet with Aran Clausen.\\
Tuesdays at 5:15 - Optional extra meeting time.\\
Wednesdays at 3:00 - Attend class.\\
Friday at 3:00 - Regular meeting time.\\

\begin{tabularx}{\textwidth}{|X|l|}
	\hline
	\textbf{Item} & \textbf{Due}\\
	\hline
	Requirements Development Process & 4/23/14\\ \hline
	Team Work Plan & 4/23/14\\ \hline
	Requirements Management Process & 4/30/14\\ \hline
	Vision and Scope Document & 4/30/14\\ \hline
	Use Case Definitions & 5/7/14\\ \hline
	Software Life Cycle Definition & 5/7/14\\ \hline
	Software Requirements Specification & 5/12/14\\ \hline
	Requirements Validation Plan & 5/12/14\\ \hline
	Requirements Tractability Matrix & 5/19/14\\ \hline
	Software Quality Assurance Plan & 5/19/14\\ \hline
	Team Presentation & 6/11/14\\ \hline
\end{tabularx}

\section{PROCESS AND QUALITY ASSURANCE}
Thomas will be primarily responsible for product quality assurance. He will review each item produced for process compliance and product quality.

\section{CONFIGURATION MANAGEMENT/BUG TRACKING}
As the Software Test Lead, Danielle will be primarily responsible for configuration management and tracking bugs in the software.

\section{REQUIREMENTS MANAGEMENT AND DEVELOPMENT}
As a team, we will write a Software Requirement Specification document as we learn from our client what is required by our product. We will contact Dr. Garfinkle as well as Dr. Hearne and Dr. Liu as questions concerning the requirements arise. Changes to the requirements must always be documented.

\section{VERIFICATION AND VALIDATION}
Each week evaluate the requirements and specifications --- verify that the two are still consistent with each other. If they are not consistent, each group member may propose revisions to the original specifications.

\end{document}
